% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.

%!TEX root = ../boktor.tex

\beginsong{Because The Night (bass)}[by=Patti Smith]


%{\nolyrics Intro: \[E] \[G] \[A]}


\beginverse
\[Bm]Take me \[G]now baby \[A]here as I \[Bm]am, \brk  \[Bm]Pull me \[G]close, try and \[A]under\[Bm]stand
\[Bm]Desirous \[G]hunger is the \[A]fire I \[Bm]breathe, \brk  \[Bm]Love is a \[G]banquet on \[A]which we \[Bm]feed
\endverse

\beginchorus
\[G]Come on \[A]now try and \[D]un\[D]der\[A]stand, \brk  The \[Bm]way I \[G]feel when I'm \[G]in \[G]your \[A]hands.
\[D]Take my \[G]hand come \[G]un\[G]der\[A]cover, \brk  They \[C]can't hurt you now, \brk  \[Bm]Can't hurt you now, \[F#]can't hurt you now.
\[Bm]Be\[Bm]cause \[G]the \[G]night be\[G]longs \[A]to \[A]lovers, \brk  \[Bm]Be\[Bm]cause the \[G]night be\[G]longs \[A]to \[Bm]lust.
\[Bm]Be\[Bm]cause \[G]the \[G]night be\[G]longs \[A]to \[A]lovers, \brk  \[Bm]Be\[Bm]cause the \[G]night be\[G]longs \[A]to \[Bm]us.
\endchorus

\beginverse
\[Bm]Have I \[G]doubt \[A]when I'm a\[Bm]lone, \brk  \[...]Love is a ring, the telephone
Love is an angel disguised as lust, \brk  Here in our bed until the morning comes
\endverse

\beginchorus
\[G]Come on \[A]now try and \[D]un\[D]der\[A]stand, \brk  The \[Bm]way I \[G]feel under \[G]your \[G]com\[A]mand
\[D]Take my \[G]hand as the \[G]sun \[G]des\[A]cends, \brk  They \[C]can't touch you now, \brk  \[Bm]Can't touch you now, \[F#]can't touch you now.
\[Bm]Be\[Bm]cause \[G]the \[G]night be\[G]longs \[A]to \[A]lovers, \brk  \[Bm]Be\[Bm]cause the \[G]night be\[G]longs \[A]to \[Bm]lust.
\[Bm]Be\[Bm]cause \[G]the \[G]night be\[G]longs \[A]to \[A]lovers, \brk  \[Bm]Be\[Bm]cause the \[G]night be\[G]longs \[A]to \[Bm]us.
\endchorus

\beginverse
SOLO:
\[ G A D.D A ]
\[ Bm G G.G A]
\[ D G G.G A ]
\[ G G G G G G ... ]
\endverse

\beginverse
With \[D]love \[A]we \[A]sleep, With \[D]doubt \[A]the \[A]vicious circle
\[Bm]Turn \[A]and \[A]burns, \brk  With\[D]out \[A]you \[A]I cannot
\[Bm]Live, \[A]For\[A]give, the \[D]year\[A]ning \[A]burning
\[G]I believe \[D]it's \[D]time, too \[G]real to feel
So \[Bm]touch \[C#m]me \[D]now, \[D]touch \[E]me \[F#]now, \[G...]touch me \[F#...]now
\endverse

\beginchorus
(rep. to end)
\[Bm]Be\[Bm]cause \[G]the \[G]night be\[G]longs \[A]to \[A]lovers, \brk  \[Bm]Be\[Bm]cause the \[G]night be\[G]longs \[A]to \[Bm]lust.
\endchorus

\endsong
