% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Should I stay or should I go}[by=The Clash]

\gtab{A7}{X02020}

\beginverse*
\rep{4} {\nolyrics Intro: \[D] \[G] \[D]}
\endverse

\beginverse
Darling, you gotta let me know  \[D G D], \brk  Should I stay or should I go?  \[D G D]
If you say that you are mine  \[G F G], \brk  I'll be there till the end of time  \[D G D]
So you gotta let me know  \[A7], \brk  Should I stay or should I go?  \[D G D]
It's always tease, tease, tease, \brk  You're happy when I'm on my knees
One day is fine and the next is black, \brk  So if you want me off your back
Well, come on and let me know, \brk  Should I stay or should I go?
\endverse

\beginchorus
%\lrep \rep{2} Should I stay or should I go now?
Should I stay or should I go now?
If I go there will be trouble, \brk  And if I stay it will be double
So come on and let me know 
%So come on and let me know \rrep
\endchorus

\beginverse
This indecision's bugging me  \brk   \echo{Esta indecision me molesta}
If you don't want me set me free  \brk  \echo{Si no quieres librame}
Exactly who I'm supposed to be  \brk  \echo{Digame que tengo ser}
Don't you know which clothes even fits me?  \brk  \echo{Sabes que ropa me queda}
Come on and let me know  \brk  \echo{Me tienes que decir}
Should I cool it or should I blow?  \brk  \echo{Me debo ir o quedarme}
\endverse

\beginverse
(couplet zonder samenhangende zang, wat Spaans geloei...)
\endverse

\beginchorus
\lrep \rep{2:} Should I stay or should I go now?
If I go there will be trouble, \brk  And if I stay it will be double
So come on and let me know \rrep, \brk  Should I cool it or should I blow?  
\endchorus


\endsong
