% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Hit The Road Jack}[by=Ray Charles]


%{\nolyrics Intro: \[E] \[G] \[A]}


\beginverse
intro: \[ Am G F E ]
\endverse

\beginchorus
\echo{Hit the road Jack and don't you come back no more, no more, no more, no more.}
\echo{Hit the road Jack and don't you come back no more.}, \brk  What you say?
\echo{Hit the road Jack and don't you come back no more, no more, no more, no more.}
\echo{Hit the road Jack and don't you come back no more.}
\endchorus

\beginverse
Woah Woman, oh woman, don't treat me so mean,
You're the meanest old woman that I've ever seen.
I guess if you said so
I'd have to pack my things and go. \echo{That's right}
\endverse

\beginchorus
REF
%\echo{Hit the road Jack and don't you come back no more, no more, no more, no more.}
%\echo{Hit the road Jack and don't you come back no more.}, \brk  What you say?
%\echo{Hit the road Jack and don't you come back no more, no more, no more, no more.}
%\echo{Hit the road Jack and don't you come back no more.}
\endchorus

\beginverse
Now baby, listen baby, don't ya treat me this-a way
Cause I'll be back on my feet some day.
\echo{Don't care if you do 'cause it's understood}
\echo{you ain't got no money you just ain't no good.}
Well, I guess if you say so
I'd have to pack my things and go. \echo{That's right}
\endverse

\beginchorus
REF
%\echo{Hit the road Jack and don't you come back no more, no more, no more, no more.}
%\echo{Hit the road Jack and don't you come back no more.}, \brk  What you say?
%\echo{Hit the road Jack and don't you come back no more, no more, no more, no more.}
%\echo{Hit the road Jack and don't you come back no more.}
\endchorus

\beginverse
Well, \brk  \echo{don't you come back no more.}
Uh, what you say?, \brk  \echo{don't you come back no more.}
I didn't understand you, \brk  \echo{don't you come back no more.}
You can't mean that, \brk  \echo{don't you come back no more.}
Oh, now baby, please, \brk  \echo{don't you come back no more.}
What you tryin' to do to me?, \brk  \echo{don't you come back no more.}
Oh, don't treat me like that, \brk  \echo{don't you come back no more.} 
\endverse


\endsong
