% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.

%!TEX root =


\beginsong{American Tune}[by={Paul Simon}]

%\gtab{D}{XX0232}

%\beginverse*
%intro \rep{2}:   \[ G2 \ F# \ Bm \ A2 \ Dsus2  ]
%\endverse

\beginverse
\[C]Many's the \[F]time \[C]I've \[G]been \[C]mis\[G]ta\[E7]ken, and \[Am]many \[E7]times con\[Am]fused.
And I've \[F]of\[C]ten \[G]felt \[C]for\[G]sa\[E7]ken, and \[Am]certain\[E7]ly mis\[Am]used.
But it's \[F]all \[G]right, it's \[F]all \[C]right, just \[F]weary \[C]to my \[E7]bones.
\[F] Still, you \[G]don't expect to be, \[C]bright and \[D]Bon Vi\[G]vant.
So \[F]far a\[G]way from \[E7]home, \[F] so \[C]far a\[G]way from \[C]home.
\endverse

\beginverse
I \[C]don't know a \[F]soul \[C]who's \[G]not \[C]been \[G]bat\[E7]tered, Don't have a \[Am]friend who \[E7]feels at \[Am]ease.
\[C]Don't know a \[F]dream \[C]that's \[G]not \[C]been \[G]shat\[E7]tered, Or \[Am]driven \[E7]to its \[Am]knees.
But it's \[F]all \[G]right, it's \[F]all right, all \[C]right, We've \[F]lived so \[C]well so \[E7]long.
\[F] Still, \[G]when I think of the \[C]road we're \[D]traveling \[G]on,
I \[F]wonder \[G]what went \[E7]wrong, \[F] can't help but \[C]wonder \[G]what went \[C]wrong.
\endverse

\beginverse
And I dreamed I was \[C]flying. I dreamed that my \[G]soul rose unex\[Am]pectedly, \[F#4.5]
looking back \[G]down on me, \[F]smiled reas\[C]suring\[G]ly,
and I dreamed I was \[C]dying. And far \[G]above, my eyes could \[Am]clearly see,
The Statue of \[G]Liberty, \[F] drifting a\[C]way to \[G]sea.
And I dreamed I was \[C]flying.
\endverse

\beginverse
We come on a \[F]ship \[C]we \[G]call \[C]May\[G]flo\[E7]wer, We come on a \[Am]ship that \[E7]sailed the \[Am]moon,
We come at the \[F]a\[C]ges \[G]most \[C]un\[G]certain \[E7]hour, And \[Am]sing the A\[E7]merican \[Am]tune,
But it's \[F]all \[G]right, it's \[F]all right, all \[C]right, You \[F]can't be \[C]forever \[E7]blessed,
\[F]Still, to\[G]morrow's gonna be a\[C]nother \[D]working \[G]day, And I'm \[F]trying to \[G]get some \[E7]rest,
\[F]That's all, I'm \[C]trying to \[G]get some \[C]rest.
\endverse


\endsong
