% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Amy }[by=Green Day]
%\gtab{B&}{X133XX}
\transpose{-2}
%\minfrets=5
%\gtab{Bm}{224432}
%\gtab{F#m}{244222}
%\gtab{D}{XX0232}
%\gtab{G}{320003}
%\gtab{A}{002220}
%\gtab{Gm}{355333}
\capo{6?}
\preferflats
\beginverse* 
Intro: \[ \ Bm \  F#m \  Bm \  F#m ]
\endverse

\beginverse
\[D] Is your heart singing \[Bm]out of tune?  \brk  Are your \[G]eyes just singing the bl\[D]ues?
\[D] Dirty records from an\[Bm]other time,   \brk   Some bl\[G]ood stains on your sh\[A]oes

\[D] No one really knows ab\[Bm]out your soul,   \brk   And I \[G]barely really know your n\[D]ame
\[D] Burning rhythms and p\[F#m]osting lies,   \brk   And a b\[G]unch of fools dr\[A]own in sh\[D]ame
\endverse

\beginchorus
Amy don't you \[Bm]go,   \brk   I want you a\[D]round, \brk Singin' \[Bm]woah \[F#m]please don't go
Do you \[G]wanna be a \[A]friend of \[D]mine?, \brk Do you \[G]wanna be a \[A]friend of \[Bm]mine? \ \[ F#m Bm F#m] 
\endchorus

\beginverse
\[D]Did you tattoo a \[Bm]lucky charm,   \brk   To \[G]keep you out of harms \[D]way?
\[D]Warding off all \[F#m]evil signs,   \brk   But \[G]never really \[A]kept you safe
\[D]Now you're too young for the \[Bm]golden age,   \brk   'Cause the \[G]record bin's been re\[D]placed
\[D]27 gone with\[F#m]out a trace,   \brk   And you \[G]walked away \[A]from your \[D]drink
\endverse

\beginchorus
Amy don't you g\[Bm]o,   \brk   I want you ar\[D]ound, \brk Singin' w\[Bm]oah pl\[F#m]ease don't go
Do you \[G]wanna be a \[A]friend of m\[D]ine?, \brk Do you \[G]wanna be a \[A]friend of...
\[C]Amy please don't \[G]go! \[Gm], \brk \[C]Amy please don't \[G]go! \[A]
\endchorus

\beginverse
\[D] Is your heart singing \[Bm]out of tune?  \brk  Are your \[G]eyes just singing the bl\[D]ues?
\[D] Dirty records from an\[Bm]other time,   \brk   Some bl\[G]ood stains on your sh\[A]oes
\[D]May I have this \[Bm]last dance   \brk   By \[G]chance if we should \[D]meet?
\[D]Can you write me a \[F#m]lullaby?   \brk   So we \[G]can sing \[A]you to \[D]sleep
\endverse

\beginchorus
Amy don't you \[Bm]go,   \brk   I want you \[D]around, \brk Singin' w\[Bm]oah pl\[F#m]ease don't go
(2x): Do you \[G]wanna be a \[A]friend of \[D]mine?
Do you \[G]wanna be a \[A]friend of \[Bm]mine?  \[ F#m \ Bm \ F#m ]
\endchorus

\endsong
