% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.

%!TEX root = ../boktor.tex

\beginsong{Maggie May}[by=Rod Stewart]

\begin{LARGE}

%\beginchorus
%intro: \rep{2}:  \[C] \[Am]
%\endchorus
\chordsoff
\beginverse
Wake up Maggie, I think I got something to say to you
it's late September and I really should be back at school.
I know I keep you amused, but I feel I'm being used
oh, Maggie, I couldn't have tried anymore.
You led me away from home, just to save you from being alone.
You stole my heart and that's what really hurts.
\endverse

\beginverse
The morning sun, when it's in your face, really shows your age
but that don't worry me none, in my eyes you're everything.
I laughed at all of your jokes, my love you didn't need to coax
oh, Maggie, I couldn't have tried anymore.
You led me away from home, just to save you from being alone.
You stole my soul, that's a pain I can do without.
All I needed was a friend, to lend, a guiding hand
but you turned into a lover, and Mother, what a lover!
\endverse

\beginverse
You wore me out. All you did was wreck my bed
and in the morning kick me in the head
oh, Maggie, I couldn't have tried anymore.
You led me away from home, 'cause you didn't want to be alone.
You stole my heart, I couldn't leave you if I tried.
\endverse

\beginverse
SOLO
\endverse

\beginverse
I suppose I could collect my books and get on back to school.
Or steal my daddy's cue and make a living out of playing pool.
Or find myself a rock and roll band, that needs a helpin' hand.
Oh, Maggie, I wish I'd never seen your face.
you made a first-class fool out of me, but I'm as blind as a fool can be.
you stole my heart but I love you anyway.
\endverse

\beginverse
SOLO
\endverse
\beginverse
Maggie, I wished I'd never seen your face
I'll get on back home, one of these days
\endverse



\end{LARGE}

%\chordsoff

\chordson
\endsong
