% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Rhiannon }[by=Fleetwood Mac]


%{\nolyrics Intro: \[E] \[G] \[A]}


\beginverse
INTRO:  \[ Am  F ] (2x)
\endverse

\beginverse
\[Am]Rhiannon rings like a bell through the night,  \brk  And \[F]wouldn't you love to love her?
\[Am]Takes to the sky like a bird in flight,  \brk  And \[F]who will be her lover?
\[C]All your life you've never seen a \[F]woman taken by the wind
\[C]Would you stay if she promised to you heaven?
\[F]Will you ever win?
\endverse

\beginverse
She is like a cat in the dark and then ,  \brk  She is the darkness
She rules her life like a fine skylark and when ,  \brk  The sky is starless
All your life you've never seen a woman taken by the wind
Would you stay if she promised to you heaven?
\[F]Will you ever win?,  \brk  Will you ever win?
\endverse

\beginchorus
Rhiannon,  \brk  Rhiannon,  \brk  Rhiannon,  \brk  Rhiannon
\endchorus

\musicnote{tussenloopje}

\beginverse
She rings like a bell through the night,  \brk  And wouldn't you love to love her?
She rules her life like a bird in flight,  \brk  And who will be her lover?
All your life you've never seen a woman taken by the wind
Would you stay if she promised to you heaven?
Will you ever win?
Will you ever win?
\endverse

\beginchorus
Rhiannon,  \brk  Rhiannon,  \brk  Rhiannon
\endchorus

\beginchorus
Oooooh
\[F]Taken by,  \brk  Taken by the sky \[Am]    (3x)
(dan 1x nstrumentaal)
\endchorus

\beginchorus
Dreams unwind,  \brk  Love's a state of mind    (3x)
\endchorus


\endsong
