% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Troy}[by=Sinead o' Connor]

\capo{3}

%{\nolyrics Intro: \[E] \[G] \[A]}


\beginverse
intro: \[Am] \[G] 
\[Am]I'll re\[G]member it, \brk  \[Am]Dublin in a \[G]rainstorm, \brk  \[Am]sitting in the \[G]long grass in summer, \brk  \[Am]Keeping \[G]warm. 
\[Am]I'll re\[G]member it, \brk  \[Am]Every restless \[G]night, \brk  \[Am]We were \[G]so young then, We thought that \[Am]everything, \brk  We could possibly do was \[G]right. 
\[Am]Then we \[G]moved, \brk  \[Am]Stolen from our very \[G]eyes, \brk  \[Am]And I wondered where you \[G]went to, \brk  Tell \[Am]me when did the \[G]light die.
\[Am]You will \[G]rise, \brk  \[Am]You'll re\[G]turn, \brk  \[Am]The phoenix from the \[G]flame, \brk  \[Am]You will \[G]learn, \brk  , \brk  \[Am]You will \[G]rise, \brk  \[Am]You'll \[G]return, \brk \[Am]. 
Being what you \[C]are, \brk  There is no other \[Am]Troy, \brk  For you to \[G]burn \[E]. 
\endverse

\beginverse
\[Am]And I never meant to \[G]hurt you, \brk  I \[Am]swear , I didn't mean those things I \[G]said. 
\[Am] I never meant to \[G]do that to you, \brk  Next time I'll \[Am]keep my hands to myself \[G]instead
\[Am]Oh, does she \[G]love you, \brk  \[Am]What do you \[G]want to do?, \brk  \[Am]Does she \[G]need you like I \[Am]do?   \[G] 
\[Am]Do you \[G]love her?, \brk  \[Am]Is she \[G]good for you?, \brk  \[Am]Does she \[G]hold you like I \[Am]do? \[G] .
\[Am]Do you \[G]want me?, \brk  \[Am]Should I \[G]leave?, \brk  \[Am]I know you're always \[G]telling me, \brk  That you love me, Just sometimes I wonder, \brk  If I should believe. 
\[Am]Oh, I \[G]love you, \brk  \[Am]God, I \[G]love you, \brk  \[Am]I'd kill a dragon for you. 
I'll \[G]die, \brk  \[Am]But I will \[G]rise, \brk  \[Am]And I will re\[G]turn, \brk  \[Am]The Phoenix from the \[G]flame
\[Am]I have \[G]learned, \brk  \[Am]I will \[G]rise, \brk  \[Am]you'll see me re\[G]turn
Being what I \[C]am, \brk  There is no other \[Am]Troy, \brk  For me to \[G]burn  \[E] 
\endverse

\beginverse
\[Am]And you should've left the \[G]light on, \brk  \[Am]You should've left the \[G]light on. 
\[Am]Then I wouldn't have tried, \brk  And you'd \[G]never have known. 
\[Am]And I wouldn't have pulled you \[G]tighter, \brk  \[Am]No I wouldn't have pulled you \[G]close. 
\[Am]I wouldn't have \[G]screamed, \brk  No I can't let you \[Am]go. 
And the door wasn't closed  \[G] , \brk  No \[Am]I wouldn't have pulled you to \[G]me, \brk  No \[Am]I wouldn't have kissed your \[G]face
\[Am]You wouldn't have \[G]begged me to hold you, \brk  If we hadn't been \[Am]there in the first \[G]place. 
Ah but \[Am]I know you wanted me to \[G]be there oh \[Am]oh \[G], \[Am]Every look that you threw \[G]told me so. 
\[Am]But you should've left the \[G]light on, \brk  \[Am]You should've left the \[G]light on
\[Am]And the flames burned \[G]away, \brk  But you're still spitting fire, \brk  Make no difference what you say
\rep{3} You're still a liar
\endverse


\endsong
