% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Jersey Girl}[by=Tom Waits]


\beginchorus
{\nolyrics Intro: \rep{2} \[C G D G ]  }
\endchorus

\beginverse
Got no time for the corner boys, down in the street makin' all that noise,
Don't want no whores on eighth avenue, cause tonight i'm gonna be with you.
Cause tonight I'm gonna take that ride, cross the river to the jersey side,
Take my baby to the carnival, and I'll take you on all the rides, 
Down the shore everything's alright, you with your baby on a saturday night,
Don't you know all my dreams come true, when I'm walkin' down the street With you, 
Sing sha la la la la la sha la la la.
Sha la la la la I'm in love with a Jersey girl. 
Sing sha la la la la la sha la la la.
Sha la la la la. 
\endverse

\beginverse
You know she thrills me with all her charms, when I'm wrapped up in my baby's arms, 
My little angel gives me everything, I know someday that she'll wear my ring.
So don't bother me cause i got no time, I'm on my way to see that girl of Mine, 
Nothin' else matters in this whole wide world, when you're in love with a jersey girl, 
Sing sha la la la la la la.
Sha la la la la I'm in love with a Jersey girl. 
Sing sha la la la la la sha la la la.
Sha la la la la. 
\endverse

\beginverse
And I call your name, I can't sleep at night, 
Sha la la la la la la. 
\endverse


\endsong
