% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{Holiday }[by=Green Day]


%{\nolyrics Intro: \[E] \[G] \[A]}


\beginverse
Say, hey!

Hear the sound of the falling rain, \brk  Coming down like an Armageddon flame  \echo{Hey!}
The shame, \brk  The ones who died without a name

Hear the dogs howling out of key, \brk  To a hymn called "Faith and Misery" \echo{Hey!}
The company lost the war today
\endverse

\beginchorus
I beg to dream and differ from the hollow lies, \brk  This is the dawning of the rest of our lives, 
On holiday
\endchorus

\beginverse
Hear the drum pounding out of time, \brk  Another protester has crossed the line \echo{Hey!}
To find, the money's on the other side

Can I get another Amen? \echo{Amen!}, \brk  There's a flag wrapped around a score of men \echo{Hey!}
A plastic bag on a monument
\endverse

\beginchorus
I beg to dream and differ from the hollow lies, \brk  This is the dawning of the rest of our lives, 
On holiday
\endchorus

\beginverse
[SOLO] \[C G D Em]
\endverse

\beginverse
(Hey!)
(Say, hey!)

"The representative from California has the floor"

Zieg Heil to the president Gasman, \brk  Bombs away is your punishment
Pulverize the Eiffel towers, \brk  Who criticize your government
Bang bang goes the broken glass and, \brk  Kill all the fags that don't agree
Trials by fire, setting fire, \brk  Is not a way that's meant for me
Just cause (hey, hey, hey), just cause, because we're outlaws yeah!
\endverse

\beginchorus
I beg to dream and differ from the hollow lies, \brk  This is the dawning of the rest of our lives
I beg to dream and differ from the hollow lies, \brk  This is the dawning of the rest of our lives
This is our lives on holiday 
\endchorus

\endsong
