% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.

%!TEX root = ../tucktheman.tex

\beginsong{Tuck the man}[by=Hallo Venray]

%\capo{3}

%{\nolyrics Intro: \[E] \[G] \[A]}





\beginverse
Intro: Am (met/zonder)
\endverse

\beginverse
\[Am]Tuck is a man. And he \[Dm]likes to be a man. 
And he \[F]knows he can love a woman that \[Am]way. 
\endverse

\beginverse
\[Am]Tuck wants to be an actor. He doesn't \[Dm]mention it that much. 
And he \[F]says it's a dream but it doesn't \[Am]pay. 
\endverse

\beginverse
\[Am]Tuck was good at school. That's where he \[Dm]met his first girlfriend. 
And he's \[F]still with her, up to this day. 
\endverse

\beginverse
\[Am]Tuck has a job. And he \[Dm]likes to work hard. 
And he \[F]knows he can pay the bills he has to \[Am]pay. 
\endverse

\beginchorus
\[Am]One day, I'm gonna be an actor, and Sing a song to the girl I'm after, 
\[Am]I'll be waiting so long, I want to have her, 
\[Am]And my love is so strong, I'll die if I won't get her, 
And when I  \[F]get to her lips, she'll give a kiss, 
And fill the emptiness, we felt, so long in hour \[Am]hearts.
\[Dm]She'll be the one with the sun in her eyes. 
\[F]She'll be the one with the sun in her eyes. 
\[C]She'll \[G]be the \[Dm]one with the sun in her eyes. 
\endchorus

\beginverse
\[Am]Tuck is a man. And he \[Dm]likes to be a man. 
And he \[F]knows he can love a woman that \[Am]way. 
\endverse

\beginverse
\[Am]Tuck wants to be an actor. He doesn't \[Dm]mention it that much. 
And he \[F]says it's a dream but it doesn't \[Am]pay. 
\endverse

\beginverse
\[Am]Tuck is doing the best he can, And he \[Dm]says doing less, 
Would be \[F]wrong, the wrong thing to do. 
\endverse



\endsong
