% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.

%!TEX root = ../boktor.tex

\beginsong{Night like this }[by=Caro Emerald]
%\gtab{G}{320033}
%\gtab{C}{032010}
%\gtab{E}{022100}
%\gtab{E7}{020100}
%\capo{2}

%\transpose{-3}

\beginverse
From where you \[Cm]are, You see the smoke start to arise where they play \[G]cards.
And you walk over, softly movin' past the guards.
The stakes are gettin' higher, you can \[Cm]feel it in your heart.
He calls your bluff, He is the ace, you never thought he'd play that \[G]much.
And now it's more than all these cards you want to touch.
You'll never know if winnin' this could \[Cm]really be enough.
Take a \[Dm7-5]look beyond the \[G]moon you'll see the \[Cm]stars.
And \[Dm7-5]when you look around, You \[G]know the room by \[C]heart.
\endverse

\beginchorus
I have never \[G]dreamed it, Have you ever dreamed a night like \[C]this?
I cannot \[G]believe it, I may never see a night like \[C]this.
When everything you \[G]think is incomplete, Starts happening when \[C]you are cheek to cheek.
Could you ever \[G]dream it? I have never dreamed, Dreamed a night like \[Cm]this.
\endchorus

\beginverse
How many \[Cm]times, Have I been waiting by the door to hear these \[G]chimes?
To hear that someone debonair has just arrived.
And opened up to see my \[Cm]world before my eyes.
That silhouette, Creates an image and a night I can't for\[G]get.
It has the scent of something special, I can't rest.
If I resist temptation, oh, I \[Cm]know for sure that I will lose the bet.
I \[Dm7-5]walk away and suddenly it \[G]seems I'm not \[Cm]alone.
In \[Dm7-5]front of me he stands, I \[G]stop before he \[C]goes.
\endverse

\beginchorus
Refrein
\endchorus

\beginchorus
[Instrumental Break] \[Ebm  D  Db  Cm  Ebm  D  Db  C]
\endchorus

\beginchorus
Refrein
\endchorus

%\beginverse*
%\[ G F C G F C ]
% \[Dm] She just left me, oh, And there's no one here that I\[C], Want to change her for
%\endverse

\endsong
