% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root = ../boktor.tex 

\beginsong{The Show Must Go On }[by=Famous Last Words]


%{\nolyrics Intro: \[E] \[G] \[A]}


\beginverse
I must accept these consequences for my actions,
When all I did was what the world told me I should do.
And do anything for my dreams, if only I knew
The cost of my dreams AKA you, would be you.
I'm dead now!
\endverse

\beginchorus
The nightmare,   \brk   Is slowly taking over,
All that's happened,   \brk   It is enabling him
To take exactly what he wants,   \brk   Until he gets what he desires,
We'll be at his whim.
\endchorus

\beginchorus
My inner demon, he is screamin' at me, "Take her now!
This is your only chance, won't get another, don't let me down!
Don't fucking whine, the deed is done you'll be just fine.
So you want true romance? Throw the dice, take a chance."
\endchorus

\beginverse
Why won't you let me in? Just let me in!
We'll masquerade this awkward phase that we're stuck in!
If you accept me and forever be by my side,
Remember what I said? Every day's a new sunrise.
So let's just act pretend like this never happened,
I'm your arcane guardian,
Just let me in.
\endverse

\beginchorus
You know our love is caught in your eyes.
And those hazel eyes,  \brk  They terrorize, they terrorize!
\endchorus

\beginchorus
My inner demon, he is screamin' at me, "Take her now!
This is your only chance, won't get another, don't let me down!
Don't fucking whine, the deed is done you'll be just fine.
So you want true romance? Throw the dice, take a chance."
\endchorus

\beginchorus
Don't let me down,   \brk   If I can't have you, I will never be found.
It's sure to kill me if you leave me,  \brk  So I'll leave you gagged and bound.
I won't reside, never abide,
I won't live my life caught in a lie.
\endchorus

\beginverse
Baby, don't scream.
Don't scream, you are not alone!
His arms are not your new home.
Now just close your eyes, you will never say goodbye!
Baby don't scream.
You know I did this all for you and me!
Tell me why!
Don't fucking scream, you know I did this all just for me!
\endverse

\beginchorus
You know our love is caught in your eyes
And those hazel eyes,  \brk  They terrorize, they terrorize!
\endchorus

\beginverse
Don't let me down
If I can't have you, I will never be found.
It's sure to kill me if you leave me,
So I'll leave you gagged and bound.
I won't reside, never abide,
I won't live my life caught in a lie.
\endverse

\beginchorus
There's no escape, from this place!
But somehow you unlocked all the chains.
Paralyzed in authentic fear,
Cause I'm insane, and I'm deranged.
You mustn't share twisted affairs with all your peers,
So I'll push you down the stairs,
And lock you down there in the dark for years!
\endchorus

\beginverse
[Outro]
This cannot be, it must be a dream!
I can't bare this harsh reality.
She's my only destiny.
We must create, our own fate,
I took her life, now it's too late.
(This Darkness
Has overcome your common sense
Be honest
Impulsive actions made a mess
This darkness
Like a fire burning red
So vicious
A heartless monster not a man)
\endverse

\beginchorus
I watched their lust, it sparked alive
And it tore me up inside
I will admit I'm terrified,
Let jealousy serve as my guide
I can't reside, I can't abide
Can't live my life caught in this lie
So I must die, goodbye goodnight!
\endchorus


\endsong
